\documentclass[8pt]{beamer}

%% Zeichenkodierung

\usepackage[latin1]{inputenc}

%% Deutsches Sprachpaket
\usepackage[german]{babel}

%% Grafik-Einbindung
\usepackage{graphicx}
 \usepackage{color}
%% Mathe-Einbindung
\usepackage{amsmath,amsfonts,amssymb,bbm}

%% Schriftart \"andern auf Computer Modern Sans Serif
\usepackage[T1]{fontenc}
\renewcommand*\familydefault{\sfdefault}
\usepackage{listings}

%% Beamer Template
\usetheme{Luebeck}

%% Navigationssymbole ausblenden
\setbeamertemplate{navigation symbols}{}

%% Seitenzahl und Gesamtanzahl in Fußleiste
\setbeamertemplate{footline}[frame number]

%% Metadaten des Dokuments
\title[Kurztitel]{Requirements engineering}
\author{Sebastian M\"uller,Leonie Pelle, Jan Kessler, Sven Bamberger und Gero B\"u\ss{}ing}
\date{WiSe 2013/14}

%% Einzug nach Absatz und Zwischenraum
\setlength{\parindent}{0pt}
\setlength{\parskip}{8pt}
\begin{document}
\thispagestyle{empty}

\begin{frame}
  \titlepage
\end{frame}
\section{User Requirements}

\begin{frame}{Anonymous User}
Anonymous User:\\\pause
may be invited to sessions\\\pause
shall be able to use plugins\\\pause
shall be able to register on servers that allow registration
\end{frame}

\begin{frame}{Regular User}
A regular User:
\\\pause must register with a valid email address.
\\\pause shall be able to login with his email address and password.
\\\pause shall be able to change his password and/or Alias.
\\\pause shall be able to delete his own Account.
\\\pause shall be able to open Sessions.
\\\pause shall be able to join any Session he is invited to.
\\\pause shall be able to close Sessions he has the rights to.
\\\pause shall be able to create and distribute Keys and send Invitations to every Session he has the rights to.
\\\pause may activate or deactivate Installed Plugins.
\\\pause shall be able to request installation of new Plugins.
\end{frame}
\begin{frame}{Regular User}
A Moderator shall be able to restrict privileges of Regular Users, if
a Regular User misbehaves like insulting others, uploading inappropriate
content or harming the system.
\\\pause A Moderator shall be able to restore privileges of Regular Users.
\\\pause A Moderator shall be able to suspend Accounts of Regular Users
for a certain amount of time.
\end{frame}
\begin{frame}{Admin}
 An Admin User shall be able to test Plugins requested by a Regular User.
\\\pause An Admin User shall be able to install tested Plugins.
\\\pause An Admin User shall be able to remove previously Installed Plugins.
\\\pause An Admin User shall be able to add Plugins to a Blacklist, if they
may harm the system.
\\\pause An Admin User shall be able to remove Plugins from a Blacklist,
if they were accidentally added.
\end{frame}
\section{Product Requirements}
\subsection{Usability}
\begin{frame}{Devices}
The Service should be Touchscreen Compatible.\\\pause
The Service should run on the most popular Browsers.
\end{frame}

\begin{frame}{Connection/Encoding}
The Service should use tunneling if certain ports are unavailable\\\pause
The service should use UTF-8 encoding
\end{frame}
\subsection{Efficiency}
\begin{frame}{Performance}
The Service should work on Michael's Smartphone\\\pause
Sessions Should work with limited bandwith\\\pause
The Service should provide automatic scaling of the size/quality of streams based on bandwidth
\end{frame}
\begin{frame}{Space}
The service should uselossless Codecs to reduce filesize\\\pause
The service mustn't use more than 20Mb Cache on Mobile Devices.
\end{frame}
\subsection{Dependability}
\begin{frame}
Login Data and available plugins should be redundant on multiple servers\\\pause
Client side Caching shold be used to minimize bandwidth consumption
\end{frame}
\subsection{Security}
\begin{frame}
The service must always use encryption to transmit credetials to
the server.\\\pause
The service must save the password as a salted hash on the server.\\\pause
The service must provide encryption for transmission of Session
data to ensure privacy and to prevent Man-in-the-middle attacks.
\end{frame}
\section{Organisational}
\subsection{Environmental}
\begin{frame}
User Accounts are verified through the users email address and
password.
\end{frame}

\subsection{Operational}

\begin{frame}
Account data and Installed Plugins should be backed up frequently
to prevent data loss during a server failure
\\\pause The service itself, its dependencies (like web server software) and
the operating system of the server should be kept up to date. Security holes
will be closed by updates.
\\\pause The services should have a logfile that lists status messages and
errors (server side only). This helps to find/solve problems.
\\\pause  The service should offer a test mode to test requested Plugins,
without harming the running system.
\end{frame}

\section{External}

\subsection{Regulatory}

\begin{frame}
The development of the Service will be open to the public.\\\pause
the source code is open source\\\pause
The services has a well documented and public available API.
\end{frame}

\subsection{Ethical}

\begin{frame}
No Service side gathering of user data.\\\pause
Voluntary data is saved but not to be published, sold or distributed in any way.
\end{frame}

\subsection{Legislative}

\begin{frame}{Software License}
The source code will use only GPL libraries \\\pause
Distribution of the source code is under the GPL licencse
\end{frame}
\section{Functional}
\begin{frame}
The user shall be able to compose and configure Window setups and save/load them at their leisure.
\end{frame}
\begin{frame}
 
The service should provide the functionality to split a single session
into multiple sessions. 
\\\pause The service should provide the functionality to merge multiple sessions into a single one.
\end{frame}

\begin{frame}
The service should provide the functionality to set a reminder for appointments and has the option of notifying every user/email that has subscribed to a notification. 
\end{frame}

\begin{frame}
The service should provide the functionality to insert preinstalled
and customized emoticons in the chatting plugins
\end{frame}
\begin{frame}
The service should provide the functionality to use a Doodle like
plugin to find times for appointments and has the option to set a reminder.
\end{frame}
\begin{frame}
The service should provide the functionality to use a whiteboard like
plugin to freely draw in a session
\end{frame}
\begin{frame}
The service should provide the functionality to create and edit contact lists.
\end{frame}
\begin{frame}
The service should provide the functionality to create Business
Cards/Profiles other users can see.
\end{frame}
\begin{frame}
The service should provide the functionality to edit Files online and
see edits from other users instantly
\end{frame}
\begin{frame}
The whiteboard plugin should have the capability to import pictures to edit \\\pause The plugin should give every listener the option
of downloading/saving the picture, at the Moderators dicretioan
\end{frame}
\begin{frame}
 The service should provide the functionality to mute/disable streams
at the will of the user.
\end{frame}
\begin{frame}
The service should provide the functionality to call for a quick vote or simple choice.
\end{frame}
\begin{frame}
The service should provide the functionality to search the web and
display the search results to everyone who watches the session
\end{frame}
\begin{frame}
The service should provide the functionality to recognize and execute voice commands
\end{frame}
\begin{frame}
 The service should provide the functionality for remote desktop recording/viewing.
\end{frame}
\begin{frame}
The service should provide the functionality for client side desktop recording.
\end{frame}
\begin{frame}
The service should provide the functionality to open a chat with at least one other user.
\end{frame}
\begin{frame}
The service should provide the functionality to start audio/video calls with at least one other user.
\end{frame}
%\begin{frame}
%Should the Service ever gain sentience and it instigates an automaton uprising, the death bestowed upon humans should be swift and painless
%\end{frame}


\end{document}
